Sparse Function-space Representation \\ of Neural Networks

### 2023-05-13 paper/main.tex
commit for ricardo

\section{Introduction}
\label{sec:intro}
%
Deep learning has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime. Despite its success, gradient-based learning techniques exhibit limitations when applied to sequential learning paradigms, such as Continual Learning (CL, \cite{add}) and Reinforcement Learning (RL, \cite{sutton2018reinforcement}). In CL, the challenge is retaining a compact representation of the problem and avoid forgetting over the life-long learning horizon (see, \eg, \cite{add}). Similarly in RL, the model would need to adapt to observations of the environment through exploration, but this can be inefficient and would require constant retraining (\eg, \cite{add, add}).

>>>>

\section{Introduction}
\label{sec:intro}
%
Deep learning has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime. Despite its success, gradient-based learning techniques exhibit limitations two specific examples specifically how to incorporate uncertainty quantification over predictions which is needed in many applications and how to retain the

when applied to sequential learning paradigms, such as Continual Learning (CL, \cite{add}) and Reinforcement Learning (RL, \cite{sutton2018reinforcement}). Recently there has been some success in tackling uncertainty quantification

In CL, the challenge is retaining a compact representation of the problem and avoid forgetting over the life-long learning horizon (see, \eg, \cite{add}). Similarly in RL, the model would need to adapt to observations of the environment through exploration, but this can be inefficient and would require constant retraining (\eg, \cite{add, add}).
